Network Analysis of User-Generated Multimedia Contents:\\ A Case Study of MikuMikuDance Contents in Niconico

### 2013-12-11 paper/main.tex
more work on cascade patterns

\section{Activity Categorization}

@@

>>>>

\section{Activity Categorization} \label{activity-classification}

@@

As defined in \cite{Gruhl:2004}, a cascade is a maximal directed acyclic subgraph rooted at a node with no outgoing edges, the \emph{cascade originator}. A cascade represents how information from the cascade originator spreads to other items. Leskovec \etal~observe that cascades has two main shapes: the \emph{star} and the \emph{chain}.

In our graph, a link from one item to another is likely an indication that the linking item, in its creation, uses some piece of data from the linked item. As such, we may predict that cascade originators in our graph are likely to be modeling, choreography, and tool making items. Since data from these items can be used to create many different works, we expect that a cascade originator should generally have many items linking it. We also observed in Section~\ref{activity-classification} that there are many more CG production items which rarely provide reusable data than those that do. As a result, an item linking to a cascade originator is likely to be a CG production item and likely has no in-links. That is, we should see more stars than chains in general.

To put this hypothesis to a test, we implemented the algorithm to count cascade pattern as described in \cite{Leskovec:2006}. However, when performing graph isomorphism tests, we consider two nodes the same if and only if they have the same categories. In effect, each node in our cascade pattern can have one of the five \emph{colors} determined by its category, and two cascades are considered the same if and only if their topologies and colors match.

The distribution of the cascade patterns of the full graph is given in Figure~\ref{cascade-patterns-with-self-links}.
\begin{figure}
	\centering
	\begin{tabular}{ccccccc}
		\includegraphics[scale=0.5]{cascades_with_self_links/0001.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0002.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0003.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0004.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0005.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0006.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0007.png} \\		
		$G_1$: 5839 &
		$G_2$: 795 &
		$G_3$: 607 &
		$G_4$: 589 &
		$G_5$: 307 &
		$G_6$: 272 &
		$G_7$: 169 \\		
		\includegraphics[scale=0.5]{cascades_with_self_links/0008.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0009.png} &		
		\includegraphics[scale=0.5]{cascades_with_self_links/0010.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0011.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0012.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0013.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0014.png} \\		
		$G_8$: 129 &
		$G_9$: 102 &
		$G_{10}$: 93 &
		$G_{11}$: 88 &
		$G_{12}$: 85 &
		$G_{13}$: 72 &
		$G_{14}$: 71 \\
		\includegraphics[scale=0.5]{cascades_with_self_links/0015.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0016.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0017.png} &		
		\includegraphics[scale=0.5]{cascades_with_self_links/0018.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0019.png} &
		\includegraphics[scale=0.5]{cascades_with_self_links/0020.png} &
		& \\
		%\includegraphics[scale=0.5]{cascades_with_self_links/0021.png} \\
		$G_{15}$: 70 &
		$G_{16}$: 68 &
		$G_{17}$: 65 &
		$G_{18}$: 57 &
		$G_{19}$: 56 &
		$G_{20}$: 55 &
		%$G_{21}$: 63 
	\end{tabular}
	\caption{}
	\label{cascade-patterns-with-self-links}
\end{figure}

\begin{figure}
	\centering
	\begin{tabular}{ccccc}
		\includegraphics[scale=0.5]{cascades_no_self_links/0001.png} &
		\includegraphics[scale=0.5]{cascades_no_self_links/0002.png} &
		\includegraphics[scale=0.5]{cascades_no_self_links/0003.png} &
		\includegraphics[scale=0.5]{cascades_no_self_links/0004.png} &
		\includegraphics[scale=0.5]{cascades_no_self_links/0005.png} \\
		$G_1$: 2700 &
		$G_2$: 887 &
		$G_3$: 595 &
		$G_4$: 455 &
		$G_5$: 435 &		
		\includegraphics[scale=0.5]{cascades_no_self_links/0006.png} &
		\includegraphics[scale=0.5]{cascades_no_self_links/0007.png} &
		\includegraphics[scale=0.5]{cascades_no_self_links/0008.png} &
		\includegraphics[scale=0.5]{cascades_no_self_links/0009.png} &		
		\includegraphics[scale=0.5]{cascades_no_self_links/0010.png} \\		
		$G_6$: 191 &
		$G_7$: 184 &
		$G_8$: 138 &
		$G_9$: 134 &
		$G_{10}$: 132 &		
		\includegraphics[scale=0.5]{cascades_no_self_links/0011.png} &
		\includegraphics[scale=0.5]{cascades_no_self_links/0012.png} &
		\includegraphics[scale=0.5]{cascades_no_self_links/0013.png} &
		\includegraphics[scale=0.5]{cascades_no_self_links/0014.png} &
		\includegraphics[scale=0.5]{cascades_no_self_links/0015.png} \\		
		$G_{11}$: 121 &
		$G_{12}$: 85 &
		$G_{13}$: 84 &
		$G_{14}$: 83 &
		$G_{15}$: 74 \\		
		\includegraphics[scale=0.5]{cascades_no_self_links/0016.png} &
		\includegraphics[scale=0.5]{cascades_no_self_links/0017.png} &		
		\includegraphics[scale=0.5]{cascades_no_self_links/0018.png} &
		\includegraphics[scale=0.5]{cascades_no_self_links/0019.png} &
		\includegraphics[scale=0.5]{cascades_no_self_links/0020.png} \\
		$G_{16}$: 67 &
		$G_{17}$: 64 &
		$G_{18}$: 60 &
		$G_{19}$: 54 &
		$G_{20}$: 52 		
	\end{tabular}
	\caption{}
	\label{cascade-patterns-no-self-links}
\end{figure}
